\Huge Conferences in an Era of Expensive Carbon

### 2019-06-18 main.tex
Nit

Our first proposal is simple: Every ACM-sponsored conference should
publicly report its carbon footprint, total and per-participant. A
conference's footprint will be dominated by participants' air travel,
but the accounting should not be limited to that: It should also
include air travel to in-person PC meetings, and estimate hotel and
food CO2e costs.

We hope that a public accounting will nudge conference organizers and
attendees to change their behavior. As an analogy: Chain restaurants
in the US are required by law to post calorie counts of food items on
menu boards, and studies show that enlightened customers order, on
average, up to 50 fewer calories a day, as a
result~\cite{menu}.

>>>>

Our first proposal is simple: Every ACM-sponsored conference should publicly
report its carbon footprint (both aggregate and per-participant). Most
conferences' footprints will be dominated by their participants' air travel,
but the accounting should not be limited to that: it should also include air
travel to in-person PC meetings and estimated hotel and food CO2e footprints.

A public accounting will nudge conference organizers and
attendees to change their behavior. As an analogy: Chain restaurants
in the US are required by law to post calorie counts of food items on
menu boards, and studies show that enlightened customers order, on
average, up to 50 fewer calories a day, as a
result~\cite{menu}.
